Concurrent Programming with CXL

### 2020-06-14 book/paper.tex
Adding some appendices

\maketitle

@@

>>>>

\maketitle
\tableofcontents

@@

\appendix

\chapter{Complete List of CXL Values}

Chapter~\ref{ch:cxlvalues} provides an introduction to CXL values.
Below is a complete list of CXL value types with examples:

\vspace{1em}
\begin{tabular}{|l|l|}
\hline
Boolean & \texttt{False}, \texttt{True} \\
\hline
integers & \texttt{..., -2, -1, 0, 1, 2, ...} \\
\hline
Atom & \texttt{.example}, \texttt{.test1} \\
\hline
Program Counter & (method names are program counter constants) \\
\hline
Dictionary & \texttt{dict\{ .account: 12345, .valid: False \} } \\
\hline
Set & \texttt{\{ 1, 2, 3 \}, \{ False, .id, 3 \} } \\
\hline
Address & \texttt{\&(lock), \&(flags[2])} \\
\hline
Context & (generated by \texttt{stop} expression) \\
\hline
\end{tabular}
\vspace{1em}

Tuples, lists, strings, and bags are all special cases of dictionaries.
Both tuples and lists map indexes (starting at 0) to CXL values.
Their format is either \texttt{(e, e, ..., e,)} or
\texttt{[e, e, ..., e,]}.
If the tuple or list has two or more elements, then the final comma
is optional.
A string must be enclosed by double quotes and is represented as
a tuple of its characters.  Characters are one-character atoms.
A bag or multiset is a dictionary that maps a value to how many
times it occurs in the bag.

All CXL values are ordered with respect to one another.  First they
are ordered by type according to the table above.
So, for example, \texttt{\texttt{True} < 0 < .xyz < \{ 0 \})}.
Within types, the following rules apply:

\begin{itemize}
\item \texttt{False < True};
\item integers are ordered in the natural way;
\item atoms are lexicographically ordered;
\item program counters are ordered by their integer values;
\item dictionaries are first converted into a list of ordered (key, value)
pairs.  Then two dictionaries are lexicographically ordered by this
representation;
\item a set is first converted into an ordered list, then lexicographically
ordered;
\item an address is a list of atoms.  Addresses are lexicographically
ordered accordingly;
\item a context consists of a name tag, the value of the program counter,
the value of the register, and the contents of the stack.  Currently,
contexts are ordered by hash.
\end{itemize}

\chapter{Complete List of CXL Operators}

CXL currently supports the following operators:

\vspace{1em}
\begin{tabular}{|l|l|}
\hline
\texttt{e == e} & any two CXL values \\
\hline
\texttt{e != e} & any two CXL values \\
\hline
\texttt{e < e} & any two CXL values \\
\hline
\texttt{e <= e} & any two CXL values \\
\hline
\texttt{e > e} & any two CXL values \\
\hline
\texttt{e >= e} & any two CXL values \\
\hline
\texttt{e and e and ...} & two or more Booleans \\
\hline
\texttt{e or e or ...} & two or more Booleans \\
\hline
\texttt{not e} & a Boolean \\
\hline
\texttt{-e} & an integer \\
\hline
\texttt{e + e + ...} & two or more integers, sets, or lists \\
\hline
\texttt{e - e} & two integers or sets \\
\hline
\texttt{e * e * ...} & two or more integers or sets \\
\hline
\texttt{e / e} & two integers (integer division) \\
\hline
\texttt{e \% e} & two integers (division remainder) \\
\hline
\texttt{e~..~e} & two integers \\
\hline
\texttt{e in e} & first is any CXL value, second is set \\
\hline
\texttt{e not in e} & first is any CXL value, second is set \\
\hline
\texttt{\^{}e} & an address \\
\hline
\texttt{choose e} & a set \\
\hline
\texttt{min e} & a set \\
\hline
\texttt{max e} & a set \\
\hline
\texttt{cardinality e} & a set \\
\hline
\texttt{keys e} & a dictionary \\
\hline
\texttt{len e} & a dictionary (includes tuple or list) \\
\hline
\texttt{bagsize e} & a bag \\
\hline
\texttt{atLabel e} & atom (corresponding to a label) \\
\hline
\texttt{nametag e} & \texttt{e} must be \texttt{()} \\
\hline
\texttt{processes e} & \texttt{e} must be \texttt{()} \\
\hline
\end{tabular}
\vspace{1em}

\texttt{+} computes the union when applied to sets and
the concatenation when applied to lists or tuples.
\texttt{-} computes set difference when applied to two sets.
\texttt{*} computes the intersection when applied to sets.
\texttt{x..y} computes the set consisting of the integers \texttt{x}
through \texttt{y} inclusive.  It returns the empty set if \texttt{x > y}.

CXL also supports the following comprehensions:

\vspace{1em}
\begin{tabular}{|l|l|}
\hline
Set comprehension & \texttt{\{ f(e) for e in s \}} \\
\hline
List comprehension & \texttt{[ f(e) for e in s ]} \\
\hline
Dict comprehension & \texttt{dict\{ f(e) for e in s \}} \\
\hline
\end{tabular}
\vspace{1em}

In each case, \texttt{s} must be a set.
For list comprehensions, the list will be sorted by \texttt{e}.
For dictionary comprehensions, each \texttt{e} will be mapped to \texttt{f(e)}.
